Enter our title here

### 2017-11-02 manuscript.tex
edited

\begin{figure}
\caption{This code does this}
\begin{verbatim}[frame=single]

Student:
histogram(dataset$var_name)

@@

Student:
hist(var_name)

@@

Student:
hist(dataset$misspelled_var)

@@

@@

The \texttt{MultipleChoiceExercise}, as you would expect, contains a question and a list of various answers. Instructors write the questions in the 'lesson'
portion of the exercise and offer solutions in the 'Insructions' section. Similar to the 'normal' coding exercises, the lesson, instructions, pre-exercise 
code and SCTs have to be specified but sample and solution code do not. DataCamp offers two types of multiple choice questions: simple and regular. 
The simple multiple choice exercises are used for questions that do not require the R console or any R output. Regular multiple choice exercises 
allow instructors to pre-program objects or plots that the student needs to access to answer the question. Both types of multiple choice exercises 
are straightforward to write can act as quick checks for understanding throughout the chapter.

\begin{figure}
\caption{This code does this}
\begin{verbatim}[frame=single]
--- type:PlainMultipleChoiceExercise lang:r xp:50 skills:1 key:9707072219
## Quick check 2

@@

msg_bad <- "That is not correct"
msg_success <- "Exactly! R can do all of these things."
test_mc(correct = 4, feedback_msgs = c(msg_bad, msg_bad, msg_bad, msg_success))
```
\end{verbatim}
\label{fig:code1}
\end{figure}

>>>>

\begin{figure}
\caption{This code does this}
\begin{Verbatim}[frame=single]

Student types:
histogram(dataset$var_name)

@@

Student types:
hist(var_name)

@@

Student types:
hist(dataset$misspelled_var)

@@

\end{Verbatim}
\label{fig:code1}
\end{figure}

@@

The \texttt{MultipleChoiceExercise}, as you would expect, contains a question and a list of various answers. Instructors write the questions in the 'lesson'
portion of the exercise and offer solutions in the 'Insructions' section. Similar to the 'normal' coding exercises, the lesson, instructions, pre-exercise 
code and SCTs have to be specified but sample and solution code do not. DataCamp offers two types of multiple choice questions: simple and regular. 
The simple multiple choice exercises are used for questions that do not require the R console or any R output. Regular multiple choice exercises 
allow instructors to pre-program objects or plots that the student needs to access to answer the question. Both types of multiple choice exercises 
are straight forward to write can act as quick checks for understanding throughout the chapter.

\begin{figure}
\caption{This code does this}
\begin{Verbatim}[frame=single]
--- type:PlainMultipleChoiceExercise lang:r xp:50 skills:1 key:9707072219
## Quick check 2

@@

msg_bad <- "That is not correct"
msg_success <- "Exactly! R can do all of these things."
test_mc(correct = 4, feedback_msgs = c(msg_bad, msg_bad, msg_bad, msg_success))
```
\end{Verbatim}
\end{figure}
